Visualizing Algebraic Surfaces

### 2016-04-01 project/article/src/article.tex
backup

% bibliography management
\usepackage[backend=biber, style=alphabetic]{biblatex} 
\addbibresource{../bib/mat2000.bib}

@@

\begin{enumerate}[I.]
    \item\label{def:one} The set of all lines in $\R^3$ passing through the origin $\left( 0,
        0, 0 \right)$. Every such line meets the \emph{sphere} of radius one
        centered in the origin exactly twice, say in $P = (x, y, z)$ and its
        antipodal point $(-x, -y, -z)$.
    \item\label{def:two} The points on the sphere $S^2$, where every point $P$ and its
        antipodal points are not distinguished. For example, the point $(1, 0,
        0)$ is identified with the point $(-1, 0, 0)$.
    \item The set of equivalence classes of $\R^3 \setminus \left\{(0, 0, 0)\right\}$ where
        two points $P$ and $P^\prime$ are considered equivalent if and only if
        there is a positive $\lambda \in \R$ such that $P = \lambda P^\prime$.
\end{enumerate}

@@

\begin{defn}[The real projective plane]
    Let $\sim$ be the equivalence relation on $\R^3$ defined by
    \begin{equation}
        \notag
        (x, y, z) \sim (x', y', z') \iff (x, y, z) = \lambda(x, y, z),
    \end{equation}
    where $\lambda$ is some positive real number. Then we denote the
    equivalence class of $(x, y, z)$ as $\projp{x}{y}{z}$ and we define
    \emph{the real projective plane} as the set
    \begin{equation}
        \notag
        \proj^2(\R) = \left\{ \projp{x}{y}{z} \mid (x, y, z) \in \R^3 \setminus
        \left\{ (0, 0, 0) \right\} \right\}.
    \end{equation}
\end{defn}

@@

\begin{defn}[The real projective space of dimension $n$]\index{projective space}
    Let $\sim$ be an equivalence relation on $\R^{n+1}\setminus \left\{ \left(
    0, \ldots, 0 \right) \right\}$ defined by
    \begin{equation}
        \notag
        \left( x_1, \ldots, x_{n+1} \right) \sim \left( x_1', \ldots, x_{n+1}' \right) 
        \iff \left( x_1, \ldots, x_{n+1} \right) = \lambda \left( x_1', \ldots, x_{n+1}' \right)
    \end{equation} 
    where $\lambda$ is some positive real number. We then denote the
    equivalence class of $\left( x_1, \ldots, x_{n+1} \right)$ by
    $\projp{x_1}{\ldots}{x_{n+1}}$ and define \emph{the real projective space
    of dimension $n$} as the set
    \begin{equation}
        \notag
        \proj^n(\R) = \left\{ \projp{x_1}{\ldots}{x_{n+1}} \mid \left( x_1, \ldots, x_{n+1} \right) \in \R^{n+1} \setminus \left\{ \left( 0, \ldots, 0 \right) \right\} \right\}.
    \end{equation}

\end{defn}

@@

>>>>

% bibliography management
\usepackage[backend=biber, style=alphabetic]{biblatex} 
\usepackage[]{url} 
\urlstyle{sf}
\addbibresource{../bib/mat2000.bib}

@@

\begin{enumerate}[I.]
    \item\label{def:one} The set of all lines in $\R^3$ passing through the origin $\left( 0,
        0, 0 \right)$. Every such line meets the \emph{sphere} of radius one
        centered in the origin exactly twice, say in $P = (x, y, z)$ and its
        antipodal point $(-x, -y, -z)$.
    \item\label{def:two} The points on the sphere $S^2$, where every point $P$ and its
        antipodal points are not distinguished. For example, the point $(1, 0,
        0)$ is identified with the point $(-1, 0, 0)$.
    \item The set of equivalence classes of $\R^3 \setminus (0, 0, 0)$ where
        two points $P$ and $P^\prime$ are considered equivalent if and only if
        there is a positive $\lambda \in \R$ such that $P = \lambda P^\prime$.
\end{enumerate}

@@

\begin{defn}[The real projective plane]\index{$\proj^2(\R)$}
    Let $\sim$ be the equivalence relation on $\R^3$ defined by
    \begin{equation}
        \notag
        (x, y, z) \sim (x', y', z') \iff (x, y, z) = \lambda(x, y, z),
    \end{equation}
    where $\lambda$ is some positive real number. Then we denote the
    equivalence class of $(x, y, z)$ as $\projp{x}{y}{z}$ and we define
    \emph{the real projective plane} as the set
    \begin{equation}
        \notag
        \proj^2(\R) = \left\{ \projp{x}{y}{z} \mid (x, y, z) \in \R^3 \setminus
        (0, 0, 0) \right\}.
    \end{equation}
\end{defn}

@@

\begin{defn}[The real projective space of dimension $n$]\index{projective
    space}\index{$\proj^n(\R)$}

    Let $\sim$ be an equivalence relation on $\R^{n+1}\setminus \left( 0,
    \ldots, 0 \right)$ defined by
    \begin{equation}
        \notag
        \left( x_1, \ldots, x_{n+1} \right) \sim \left( x_1', \ldots, x_{n+1}' \right) 
        \iff \left( x_1, \ldots, x_{n+1} \right) = \lambda \left( x_1', \ldots, x_{n+1}' \right)
    \end{equation} 
    where $\lambda$ is some positive real number. We then denote the
    equivalence class of $\left( x_1, \ldots, x_{n+1} \right)$ by
    $\projp{x_1}{\ldots}{x_{n+1}}$ and define \emph{the real projective space
    of dimension $n$} as the set
    \begin{equation}
        \notag
        \proj^n(\R) = \left\{ \projp{x_1}{\ldots}{x_{n+1}} \mid \left( x_1, \ldots, x_{n+1} \right) 
        \in \R^{n+1} \setminus \left( 0, \ldots, 0 \right) \right\}.
    \end{equation}
\end{defn}

@@

Algebraic surfaces will be the central object of study in this project. We
follow the definition of \cite{cite}.
